%!TEX root = ../main.tex
\chapter{Risks}
As this is a solo development project, there is a significant risk that there will be flaws in the initial design. 
This is due to the fact - coupled with the fact that this is new technology to me - that there is a high probability that I will misunderstand what is needed for certain designs or misunderstand what the correct tool for the job is.
Because of this I would argue that during this project, it is almost certain that the initial spec for this project will change and redesigns will need to be made. 
In order to mitigate this, I have taken steps to make individual features and sections of the code of the project as modular as possible, hoping to be able to swap out sections of the code should certain changes arise.
I will also code many aspects of the app with the idea that it may move to a server back-end, rather than having data stored in the app. 
 
The risk of changes in turn raises a key risk to the project which is that it may not be ready for the deadline. 
I consider this to be a high severity risk to the project, as the hand-in date for the project is firm and unchangeable. 

As I am the only developer on the project, there is a high risk of the code quality being lower than what can be expected from a team.
I am undertaking a self code-review policy, where I reserve some time to inspect the code of each feature branch before it is merged into the master branch.
I believe that if I am sufficiently strict with the reviews, they will help me ensure that code quality is kept up to an acceptable standard.
Arrangements have also been made with a fellow course member to code review each others code as our projects are sufficiently different enough to avoid plagiarism and we both have strong interests in keeping our code quality to a high standard.
When utilized correctly, code review can find approximately 30-70\% of logic errors within a program \citep{myers2011art}.

Another risk that may arise is the potential for hardware failure. 
Should it occur, it could wipe out the codebase and the project report, effectively destroying the project. 
Whilst it is unlikely, steps must still be taken to mitigate this, and so I will store both the code and the report in multiple local and remote locations.
The report, app code and server code will all be stored on both my PC and my Laptop as a local backup, and all three will also be stored in a remote GitHub repository (Which will remain private until the deadline to avoid plagiarism).
This will ensure that should the worst occur, I will not lose any work barring the work that is yet to be uploaded.
Therefore if I make regular commits to GitHub, the deliverables of this project shall remain safe. 