%!TEX root = ../main.tex
\chapter{List of Planned Screens}
\label{appendix:screens}

\subsubsection{Your Quests Screen}
This will be a simple screen that displays the quests and potential rewards in an easy to read list.
The screen also offers a button used to mark a quest as complete, which will send this information to the Parent for confirmation before rewards are offered.

\subsubsection{Character Screen}
This screen offers a quick overview of the user's character, gold, XP and the requirements needed to level up.
This will be the first screen that a Child sees after logging in.

\subsubsection{Navigation Menu}
A navigation menu is necessary for the user to be able to change between screens with ease.
The menu will be customised to the type of user - Parent or Child - and certain options will require a Parent PIN code to gain access. 

\subsubsection{Add Quest Form}
This will be a simple screen for a Parent to input the necessary data about a quest and submit it to the server. 
The form only requires four inputs: A title for the quest; an optional longer description containing extra information; an estimated difficulty level of the task; and an expiry date.
I have opted to use a difficulty field that will tell the server what the XP/gold rewards should be, rather than having Parents manually input the rewards.
This is due to the fact that the Parent user is somewhat disconnected from the RPG elements of the application, and should see the app as more of a task management solution than a game.
I also believe that Parent users will find manually entering values of XP/gold tiresome and would find selecting a difficulty level easier. 

\subsubsection{Add Preset Quest}
This is an extension of the Add Quest form that will allow the user to automatically fill out the form by selecting a preset quest from the server.

\subsubsection{Reward Screen}
A screen that will show a list of possible real-life rewards that the Child can purchase using in game gold.